SubsidyExplorer - Step 7: Pre-Populated Proposals

### 2022-01-21 scripts/07_proposals.Rmd
comparing new vs. old proposals

# Directories for the output files generated by this script
results_dir <- paste0(here::here("results", "07-proposals/"), "mgmt_threshold_", managed_cutoff, "/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

@@

```{r}
# Proposal settings
#proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings.csv"), stringsAsFactors = F)
proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_v2.csv"), stringsAsFactors = F)

@@

@@

   ### Find fleets
    fleet <-  CreateFleets(
      vessel_list = vessel_dat,
      iuu = iuu,
      oa = oa,
      overcap = overcap,
      cap_tier = cap_tier,
      managed_threshold = managed_cutoff,
      subsidy_types_all = subsidy_types_sorted_sumaila,
      cap_tier_lookup = cap_tier_lookup_table,
      country_lookup = country_dependencies)

>>>>

# Directories for the output files generated by this script
results_dir <- paste0(here::here("results", "07-proposals/"), "mgmt_threshold_", managed_cutoff, "_2022/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

@@

```{r}
# Proposal settings
#proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings.csv"), stringsAsFactors = F)
# proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_v2.csv"), stringsAsFactors = F)
proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_v3.csv"), stringsAsFactors = F)

@@

# S&DT lookup table
sdt_lookup_table <- read_csv(here::here("app", "data", "sdt_lookup_table.csv"))

@@

   ### Find fleets
    fleet <-  CreateFleets(
      vessel_list = vessel_dat,
      iuu = iuu,
      oa = oa,
      overcap = overcap,
      cap_tier = cap_tier,
      managed_threshold = managed_cutoff,
      subsidy_types_all = subsidy_types_sorted_sumaila,
      cap_tier_lookup = cap_tier_lookup_table,
      country_lookup = country_dependencies,
      sdt_lookup = sdt_lookup_table)
